MAPCLUST - СЕРВИС ДЛЯ ЭПИДЕМИОЛОГИЧЕСКОГО И ЭКОЛОГИЧЕСКОГО МОНИТОРИНГА

### 2023-03-29 article/article.qmd
fixed csl file, sorting by appearance

---
title: "MAPCLUST - СЕРВИС ДЛЯ ЭПИДЕМИОЛОГИЧЕСКОГО И ЭКОЛОГИЧЕСКОГО МОНИТОРИНГА"
author: "Смирнов Антон Сергеевич^1^,Захаров Олег Станиславович^1^,Пятницкий Алексей Михайлович^1^, Гукасов Вадим Михайлович^2^"
toc: true
toc-depth: 3
bibliography: references.bib
csl: gost2.csl
tbl-cap-location: top
toc-title: "Оглавление"
fontsize: 14pt
engine: knitr
linestretch: 1.5
geometry:
  - top=10mm
  - left=20mm
  - right=20mm
  - heightrounded
format:
  docx:
    toc: false
  pdf:
    documentclass: article
    pdf-engine: xelatex
    header-includes: |
      \usepackage[utf8]{inputenc}
      \usepackage[american,russian]{babel}
      \usepackage{hyperref}  
      \usepackage{unicode-math}
mainfont: Arial
monofont: Arial
sansfont: Arial
editor: visual
---

>>>>

---
title: "MAPCLUST - СЕРВИС ДЛЯ ЭПИДЕМИОЛОГИЧЕСКОГО И ЭКОЛОГИЧЕСКОГО МОНИТОРИНГА"
author: "Смирнов Антон Сергеевич^1^,Захаров Олег Станиславович^1^,Пятницкий Алексей Михайлович^1^, Гукасов Вадим Михайлович^2^"
toc: true
toc-depth: 3
bibliography: references.bib
csl: gost-num-appear.csl
tbl-cap-location: top
toc-title: "Оглавление"
fontsize: 14pt
engine: knitr
linestretch: 1.5
geometry:
  - top=10mm
  - left=20mm
  - right=20mm
  - heightrounded
format:
  docx:
    toc: false
  pdf:
    documentclass: article
    pdf-engine: xelatex
    header-includes: |
      \usepackage[utf8]{inputenc}
      \usepackage[american,russian]{babel}
      \usepackage{hyperref}  
      \usepackage{unicode-math}
mainfont: Arial
monofont: Arial
sansfont: Arial
editor: visual
---
